Evaluating the Quality of RDF Data Sets on

### 2015-10-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
final submission

\textbf{\emph{Constraint Language Based}.}
We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
%RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by both classical constraint languages and OWL. SPARQL, however, is considered as a low-level implementation language in this context. In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely. Declarative languages may be placed on top of SPARQL when using it as an implementation language. For these \emph{Constraint Language Based} constraints, we expect a straight-forward support in future constraint languages.

@@

To get an overview on the constraint types, we delineate concrete constraints on the three vocabularies for each set of constraint type and classify them according to their severity.

@@

%All properties, not having the same domain and range types, are defined to be pairwise disjoint
%(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
%All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
%i.e., individuals cannot be instances of multiple disjoint classes.
\textbf{\emph{RDFS/OWL Based}.}
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}):
%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}). 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
%Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
%If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
%it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
%which may indicate when the data is verbose/redundant or expressed at a too general level.
Consider the following \emph{DL knowledge base} $\mathcal{K}$:\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly. }
\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
	%&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
&{\small\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.}} \\
	&{\small\ms{\{valid,invalid\} $\sqcap$ langString,}} \\
  &{\small\ms{Variable $\equiv$ $\exists$ concept.Concept,}} \\
	&{\small\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset,}} \\
  &{\small\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table,}} \\
	&{\small\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}}
\}\\ 
\end{DL}
\end{center}

%We extend $\mathcal{K}$ by 
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept (\emph{informational}).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
%
A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%\begin{DL}
%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%\end{DL}
%Only \emph{\textcolor{red}{dcat}:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
Only \emph{qb:DataSets}, e.g., can have \emph{qb:structure} relationships to \emph{qb:DataStructureDefinitions} (\emph{error}).
\emph{Property domains} (\emph{R-25, R-26}) and \emph{property ranges} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
%Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
Only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\emph{error}) and \emph{disco:variable} relations can only point to \emph{disco:Variables} (\emph{error}).

@@

%\textbf{Constraints on Properties.}
It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
To get an overview over a study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
If an abstract and an external description are absent, however,  
a title or an alternative title should be given (\emph{warning}).
In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels (\emph{informational}).
The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.

@@

In this section, we describe our findings based on an automatic constraint checking of a large data set. Despite the large volume of the data set in general, this study only uses data for three vocabularies. As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions. The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication end of 2015.}). 
%If our findings hold generally is still to be determined, nevertheless they provide valuable insights for future developments of constraint languages.
As the evaluation is based on three vocabularies, 
we cannot make valid general statements for all vocabularies,
but we can formulate several findings to direct the further development of constraint languages.
As these findings cannot be proved yet, 
they still have to be verified or falsified
by evaluating the quality of data represented by further well-established and newly developed vocabularies.

@@

We published by today 81 constraint types that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL. 
Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

>>>>

\textbf{\emph{Constraint Language Based}.}
We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
%RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by both classical constraint languages and RDFS/OWL. SPARQL, however, is considered as a low-level implementation language in this context. In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely. Declarative languages may be placed on top of SPARQL when using it as an implementation language. For these \emph{Constraint Language Based} constraint types, we expect a straight-forward support in future constraint languages.

@@

To get an overview on the sets of constraint types, we delineate concrete constraints on the three vocabularies for each set of constraint type and classify them according to their severity.

@@

%All properties, not having the same domain and range types, are defined to be pairwise disjoint
%(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
%All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
%i.e., individuals cannot be instances of multiple disjoint classes.
\textbf{\emph{RDFS/OWL Based}.}
It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}):
%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g. 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g. \emph{xsd:string}). 
\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
%Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
%If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
%it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
%which may indicate when the data is verbose/redundant or expressed at a too general level.
Consider the following \emph{DL knowledge base} $\mathcal{K}$:\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly. }
\begin{center}
\begin{DL} 
$\mathcal{K}=\{$ 
	%&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
&{\small\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.}} \\
	&{\small\ms{\{valid,invalid\} $\sqcap$ langString,}} \\
  &{\small\ms{Variable $\equiv$ $\exists$ concept.Concept,}} \\
	&{\small\ms{DataSet $\sqsubseteq$ $\forall$ structure.DataStructureDef,}} \\
  &{\small\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme,}} \\
	&{\small\ms{$\top$ $\sqsubseteq$ $\forall$ variable.Variable}}
\}\\ 
\end{DL}
\end{center}

%We extend $\mathcal{K}$ by 
\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
Variables, e.g., should have a relation to a theoretical concept (\emph{informational}).
%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
%
A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
%\begin{DL}
%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
%\end{DL}
%Only \emph{\textcolor{red}{dcat}:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
Only \emph{qb:DataSets}, e.g., can have \emph{qb:structure} relationships to \emph{qb:DataStructureDefinitions} (\emph{error}).
\emph{Property domains} (\emph{R-25, R-26}) and \emph{property ranges} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
%Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\emph{error}) and \emph{disco:variable} relations can only point to \emph{disco:Variables} (\emph{error}).

@@

%\textbf{Constraints on Properties.}
It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
To get an overview on a study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
If an abstract and an external description are absent, however,  
a title or an alternative title should be given (\emph{warning}).
In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels (\emph{informational}).
The variable \emph{Education at pre-school}, e.g., is represented as an ordered code list without any categories.

@@

In this section, we describe our findings based on an automatic constraint checking of a large data set. Despite the large volume of the data sets in general, this study only uses data for three vocabularies. As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions. The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication end of 2015.}). 
%If our findings hold generally is still to be determined, nevertheless they provide valuable insights for future developments of constraint languages.
As the evaluation is based on three vocabularies, 
we cannot make valid general statements for all vocabularies,
but we can formulate several findings to direct the further development of constraint languages.
As these findings cannot be proved yet, 
they still have to be verified or falsified
by evaluating the quality of data represented by further well-established and newly developed vocabularies.

@@

We published by today 81 constraint types that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioral, and economic (SBE) sciences, we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL. 
Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

### 2015-10-13 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-constraints.tex
findings
final submission

\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
%
\authorrunning{} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{\{firstname.lastname\}@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{kai@informatik.uni-mannheim.de} 
}

@@

SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like SKOS are used; 
recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

@@

	\textcolor{blue}{
	\item \textbf{{\em DISCO-C-LITERAL-RANGES-02:}}
{\em disco:cumulativePercentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	}

>>>>

\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Hartmann\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
%
\authorrunning{} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{\{firstname.lastname\}@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{kai@informatik.uni-mannheim.de} 
}

@@

SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan-2008}. 
In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like SKOS are used; 
recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

@@

	\item \textbf{{\em DISCO-C-LITERAL-RANGES-02:}}
{\em disco:cumulativePercentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}

### 2015-10-13 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-evaluation.tex
findings
final submission

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
      \hline
      \emph{Missy} & \url{http://svko-missy:8181/openrdf-workbench/repositories/native-java-store/summary} \\
			\emph{DwB} & \url{http://dwb-dev.nsd.uib.no/sparql} \\
			\emph{DDA-SND} & \url{http://ddi-rdf.borsna.se/endpoint/} \\
		\end{tabular}
	\caption{DDI-RDF SPARQL Endpoints}
	\label{tab:disco-sparql-endpoints}
\end{table}

@@

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Thesauri} \\		
      \hline
    \emph{TheSoz} & \emph{Thesaurus for the Social Sciences}\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
	  \emph{STW} & \emph{Thesaurus for Economics}\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\
	  \emph{AGROVOC} & \emph{AGROVOC Multilingual agricultural thesaurus}\tablefootnote{\url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc}} \\
		\emph{UNESCO} & \emph{UNESCO Thesaurus}\tablefootnote{\url{http://skos.um.es/sparql/}} \\
		\emph{TGN} & \emph{The Getty Thesaurus of Geographic Names}\tablefootnote{\url{http://vocab.getty.edu/sparql}} \\
		\emph{EARTh} & \emph{Environmental Applications Reference Thesaurus}\tablefootnote{\url{http://linkeddata.ge.imati.cnr.it/resource/EARTh/}} \\
		\emph{ODT} & \emph{Open Data Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/OpenData}} \\
		\emph{SLD} & \emph{Spanish Linguistic Datasets}\tablefootnote{\url{http://linguistic.linkeddata.es}} \\
		\emph{SSWT} & \emph{Social Semantic Web Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/semweb}} \\
		\emph{GBA-GU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geology Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-GTS} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geologic Time Scale}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-L} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithology}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-LU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithotectonic Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GEMET} & \emph{GEneral Multilingual Environmental Thesaurus}\tablefootnote{\url{http://www.eionet.europa.eu/gemet/}} \\
		\emph{EuroVoc} & \emph{EuroVoc}\tablefootnote{\url{http://open-data.europa.eu/de/data/dataset/eurovoc}} \\
		\emph{CECCT} & \emph{Clean Energy and Climate Change Thesaurus}\tablefootnote{\url{http://data.reegle.info/thesaurus/guide}} \\
		\end{tabular}
	\caption{Thesauri Abbreviations}
	\label{tab:thesauri-abbreviations}
\end{table}

>>>>

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
      \hline
      \emph{Missy} & \url{http://svko-missy:8181/openrdf-workbench/repositories/native-java-store/summary} \\
			             & \url{www.gesis.org/missy/sparql} \\
			\emph{DwB} & \url{http://dwb-dev.nsd.uib.no/sparql} \\
			\emph{DDA-SND} & \url{http://ddi-rdf.borsna.se/endpoint/} \\
		\end{tabular}
	\caption{DDI-RDF SPARQL Endpoints}
	\label{tab:disco-sparql-endpoints}
\end{table}

@@

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Thesauri} \\		
      \hline
    \emph{TheSoz} & \emph{Thesaurus for the Social Sciences}\tablefootnote{\url{http://www.gesis.org/en/services/research/thesauri-und-klassifikationen/social-science-thesaurus/}} \\
	  \emph{STW} & \emph{Thesaurus for Economics}\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\
	  \emph{AGROVOC} & \emph{AGROVOC Multilingual agricultural thesaurus}\tablefootnote{\url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc}} \\
		\emph{UNESCO} & \emph{UNESCO Thesaurus}\tablefootnote{\url{http://skos.um.es/sparql/}} \\
		\emph{TGN} & \emph{The Getty Thesaurus of Geographic Names}\tablefootnote{\url{http://vocab.getty.edu/sparql}} \\
		\emph{EARTh} & \emph{Environmental Applications Reference Thesaurus}\tablefootnote{\url{http://linkeddata.ge.imati.cnr.it/resource/EARTh/}} \\
		\emph{ODT} & \emph{Open Data Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/OpenData}} \\
		\emph{SLD} & \emph{Spanish Linguistic Datasets}\tablefootnote{\url{http://linguistic.linkeddata.es}} \\
		\emph{SSWT} & \emph{Social Semantic Web Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/semweb}} \\
		\emph{GBA-GU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geology Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-GTS} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geologic Time Scale}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-L} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithology}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-LU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithotectonic Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GEMET} & \emph{GEneral Multilingual Environmental Thesaurus}\tablefootnote{\url{http://www.eionet.europa.eu/gemet/}} \\
		\emph{EuroVoc} & \emph{EuroVoc}\tablefootnote{\url{http://open-data.europa.eu/de/data/dataset/eurovoc}} \\
		\emph{CECCT} & \emph{Clean Energy and Climate Change Thesaurus}\tablefootnote{\url{http://data.reegle.info/thesaurus/guide}} \\
		\end{tabular}
	\caption{Thesauri Abbreviations}
	\label{tab:thesauri-abbreviations}
\end{table}
